### 2017-02-09 MSSM/MSSM.tex
Some boring caption stuff

\begin{figure}[h!]
\begin{center}
\subfloat[Muon \pT]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/pt_1_inclusive_mt_2016.pdf}}
\subfloat[Electron $\eta$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/eta_1_inclusive_et_2016.pdf}}
\end{center}
\caption{(a) \pT~of the muon in the \mutau channel and (b) $\eta$ of the electron in the \etau channel.
The gluon fusion (dashed blue line)
and b-associated (dashed purple line) signals are overlaid. The signals are normalised to 4000 times their
cross-section times branching ratio at \mA=1 TeV and \tanb=50 in the $m_{h}^{\text{mod+}}$ scenario.}
\label{fig:mt_muonpt}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\subfloat[$S/\sqrt{B}$]{\includegraphics[width=0.7\textwidth]{./MSSM/Figures/s_over_root_b_mt_m.png}}~\\
\subfloat[Size of error interval]{\includegraphics[width=0.7\textwidth]{./MSSM/Figures/mt_muons_iso_errint.png}}
\end{center}
\caption{(a) The $S/\sqrt{B}$ for \Ztautau signal and (b) the size of the error interval on 
the best--fit value of a maximum--likeihood fit to the \Ztautau signal strength,
for various selections of the $\Delta\beta$--corrected
isolation variable with a cone size of $\Delta R = 0.4$ (solid circles), 
the $\Delta\beta$--corrected isolation variable with a cone size of $\Delta R = 0.3$ (open circles),
the $\Delta\beta$--corrected isolation variable including electrons and muons in the isolation
sum, for a cone size of $\Delta R =0.4$ (upward facing triangles) and $\Delta R =0.3$ (downward facing triangles) and
the tracker--based relative isolation (solid squares).}
\label{fig:mssm_selection_mt_muons}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\subfloat[$m_{\phi} = 160$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_160_range12.png}}
\subfloat[$m_{\phi} = 2.9$ TeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_2900_range12.png}}
%\subfloat[$m_{\phi} = 1600$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_1600_range12.pdf}}
%\subfloat[$m_{\phi} = 2900$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_2900_range12.pdf}}
\end{center}
\caption{Pre--fit expected limit on $\sigma\times$BR for the gg$\phi$ production process with decay into $\Pgt\Pgt$,
as a function of tau isolation working point (from very loose to very very tight) and
of \mT~selection from \mT$<20$ GeV to \mT$<40$ GeV, normalised to the best limit in the plane, indicated by the asterisk. This is shown
for (a) $m_{\phi}$ = 160 GeV and (b) $m_{\phi}$ = 2.9 TeV. The most optimal combination of \mT~selection and 
hadronic tau isolation working point varies, with looser selections preferred at higher mass.}
\label{fig:mssm_selection_mt_taumt}
\end{figure}
~
\begin{figure}[h!]
\begin{center}
\subfloat[gg$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_gradcuts_ggH_mt.pdf}}
\subfloat[bb$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_gradcuts_bbH_mt.pdf}}
\end{center}
\caption{Pre-fit expected limits on $\sigma \times$ BR in the \mutau channel for (a) gg$\phi$ and
(b) bb$\phi$ production, for an increasingly looser \mT~selection and tau isolation working point, starting
at the tight working point and \mT$<30$ GeV in green, the medium working point and \mT$<40$ GeV in red,
the loose working point and \mT$<50$ GeV in blue and the very loose working point and \mT$<60$ GeV in black. Loosening
the tau isolation working point and \mT~selection gradually improves limits at higher mass, and
degrades them at low mass.}
\label{fig:mssm_gradcuts_mt}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\subfloat[gg$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_optimisation_mediummt40_vs_tightmt30pt20_mt_ggH_remake.pdf}}
\subfloat[bb$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_optimisation_mediummt40_vs_tightmt30pt20_mt_bbH_remake.pdf}}
\end{center}
\caption{Pre-fit expected limits on $\sigma\times$BR in the \mutau channel for (a) gg$\phi$ production and (b) bb$\phi$ production. The
limits when using the medium hadronic tau isolation working point and \mT$<40$ GeV selection using a minimum
hadronic tau \pT~selection of 20 GeV (red circles), 30 GeV (blue circles) and 40 GeV (black circles) are shown. The green
circles show the limits using tighter tau isolation working point and \mT~selection. The limits on
the gg$\phi$ production process improve at low masses when increasing the minimum hadronic tau \pT~selection,
the effect on the bb$\phi$ production process is less pronounced.}
\label{fig:mssm_tauptcut}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\subfloat[gg$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_gradcuts_ggH_et.pdf}}
\subfloat[bb$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_gradcuts_bbH_et.pdf}}
\end{center}
\caption{Pre-fit expected limits on $\sigma \times$ BR in the \etau channel for (a) gg$\phi$ and
(b) bb$\phi$ production, for an increasingly looser \mT~selection and tau isolation working point, starting
at the tight working point and \mT$<40$ GeV in green, the medium working point and \mT$<50$ GeV in red,
the loose working point and \mT$<60$ GeV in blue and the very loose working point and \mT$<70$ GeV in black. Loosening
the tau isolation working point and \mT~selection gradually improves limits at higher mass, and
degrades them at low mass.}
\label{fig:mssm_gradcuts_et}
\end{figure}
\begin{figure}[h!]
\begin{center}
\subfloat[gg$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_optimisation_mediummt50_vs_tightmt40pt20_et_ggH_remake.pdf}}
\subfloat[bb$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_optimisation_mediummt50_vs_tightmt40pt20_et_bbH_remake.pdf}}
\end{center}
\caption{Pre-fit expected limits on $\sigma\times$BR in the \etau channel for (a) gg$\phi$ production and (b) bb$\phi$ production. The
limits using the medium hadronic tau isolation working point and \mT$<40$ GeV selection using a minimum
hadronic tau \pT~cut of 20 GeV (red circles), 30 GeV (blue circles) and 40 GeV (black circles) are shown. The green
circles show the limits using tighter tau isolation working point and \mT~selection. The limits on
the gg$\phi$ production process improve at low masses when increasing the hadronic tau \pT~cut,
the effect on the bb$\phi$ production process is less pronounced.}
\label{fig:mssm_tauptcut_et}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\subfloat[gg$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_thesis_ttopt_ggH.pdf}}
\subfloat[bb$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_thesis_ttopt_bbH.pdf}}
\end{center}
\caption{Expected upper limits for (a) the gg$\phi$ process and (b) the bb$\phi$ process 
in the \tautau channel, using the 
medium (green), tight (red) and very tight working point of the tau isolation discriminator.
The pattern is roughly the same as in the \etau and \mutau channels, with looser selections preferred at high
mass.}
\label{fig:mssm_tauid_tt}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\subfloat[Reconstruction of $D_{\zeta}$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/PZeta.pdf}}
\subfloat[$D_{\zeta}$ distribution in \emu channel]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/pzeta_inclusive_em_2016.pdf}}
\end{center}
\caption{(a) reconstruction of $D_{\zeta}$ \cite{cdf-dzeta} and (b) $D_{\zeta}$ distribution in the 
\emu channel\cite{CMS-PAS-HIG-16-037}.}
\label{fig:mssm_dzeta}
\end{figure}
~\clearpage
\subsection{Categorisation}
\label{sec:mssm_eventsel_categories}
As the analysis targets both the gluon fusion
and the b--associated production modes, 
the sensitivity to the signal can be increased by categorising
based on the number of b--tagged jets in the event.

\begin{figure}[h!]
\begin{center}
\subfloat[Number of jets]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/n_jets_inclusive_mt_2016_log.pdf}}
\subfloat[Number of b--tagged jets]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/n_bjets_inclusive_mt_2016_log.pdf}}
\end{center}
\caption{(a) Number of jets and (b) number of b--tagged jets in the \mutau channel. The gluon fusion signal (dashed
blue line) and b--associated signal (dashed purple line) are overlaid on the expected background distribution. The signals
are normalised to 100 times their cross--section times branching ratio at \mA=1 TeV and \tanb=50 in the $m_{\text{h}}^{\text{mod+}}$
scenario. We can see how the signal--sensitive bins motivate the choice of categories.}
\label{fig:mssm_cats_mt}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\subfloat[QCD and signal in \tautau no b-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mttot_sigsep_tt_nobtag.pdf}}
\subfloat[\ttbar and signal in \emu b-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mttot_sigsep_em_btag.pdf}}
\end{center}
\caption{Total transverse mass distributions in (a) the no b-tag category of the \tautau
channel, for QCD and gluon fusion signal at 400 GeV and 1 and 2 TeV overlaid and (b) in the b-tag
category of the \emu channel, for \ttbar and b-associated signal at 400 GeV and 1 and 2 TeV. 
The total transverse mass variable separates the signal and these backgrounds well.}
\label{fig:mttot_sigseps}
\end{figure}

@@

\caption{\mTtot~distribution in the \ttbar enriched control region \MET>80 GeV and $D_{\zeta}<-20$ GeV in the \emu channel,

@@

\subsubsection*{Drell-Yan shape reweighting}
As the \ac{MC} samples used for the \Ztautau estimate
do not model the data well for events with high di-lepton
mass and high Z \pT, a reweighting is applied to correct for this.
These weights are derived in bins of $\PZ/\Pphotonx$ mass and \pT~
using \Zmm events in data, in such a way that they do not
change the overall Drell-Yan normalisation. The weights
are then applied to the \Ztautau and \Zellell background processes.
The mismodelling can be seen in figure \ref{fig:dyrwt}a, which
shows the observed data and expected background distribution of the \PZ \pT~in
\Zmm events. The overall effect of the reweighting, which is derived
based on the events shown in figure \ref{fig:dyrwt}a, on the \Ztautau background
shape in the no b-tag category of the \etau channel is shown in figure \ref{fig:dyrwt}b.
\begin{figure}[h!]
\begin{center}
\subfloat[\Zmm events]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/pt_tt_inclusive_zmm_2016_log_noweight.png}}
\subfloat[Effect of Drell-Yan shape reweighting on \Ztautau background]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mttot_zttweight_et_nobtag.pdf}}
\end{center}
\caption{(a) The mismodelling in the \PZ \pT~distribution as observed
in \Zmm events, used to derive the correction and (b) the impact of applying the Drell-Yan shape
reweighting on the total transverse
mass distribution of the \Ztautau background in the no b-tag category of the \etau channel.}
\label{fig:dyrwt}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\subfloat[\mutau no b-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/CMS-PAS-HIG-16-037_Figure-aux_001-a.pdf}}
\subfloat[\emu b-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/CMS-PAS-HIG-16-037_Figure-aux_003-b.pdf}}
\end{center}
\caption{The low $m_{\text{T}}^{\text{tot}}$ region in (a) the 
no b-tag category of the \mutau channel and (b) the b-tag category of the \emu channel.
This low $m_{\text{T}}^{\text{tot}}$ region is where the backgrounds
are concentrated \cite{CMS-PAS-HIG-16-037-addit}.}
\label{fig:mssm_bkgs_overview}
\end{figure}

@@

The method described so far works well in the no b-tag categories, but in the b-tag category of both channels
the \ttbar background dominates. This is illustrated in figure \ref{fig:bkgs_highmtctrl}, where
the high-\mT~region in the no b-tag category (figure \ref{fig:bkgs_highmtctrl}a) is compared with the high-\mT~region in the 
b-tag category (figure \ref{fig:bkgs_highmtctrl}b) of the \etau channel. It is clear that the \ttbar 
background is much larger than the \Wjets background in the b-tag high-\mT~control region.
For this reason the estimate of the number
of \Wjets events in this category is made with a relaxed category selection where the b-tagging
requirement itself is removed, but the jet requirements still stand. Events with at least one 
jet with \pT$>20$ GeV and with $|\eta|<2.4$, but at most one jet with \pT$>30$ GeV and $|\eta|<4.7$, are therefore selected. The final \Wjets estimate in the b-tag category signal
region is determined by the estimate given by the number of \Wjets events
estimated in the 1-jet selection, multiplied by an extrapolation factor 
$\frac{N_{\text{W,MC}}^{\text{OS,low } m_{T},\text{b-tag category}}}{N_{\text{W,MC}}^{\text{OS, low }m_{\text{T}},\text{1-jet selection}}}$.
\begin{figure}[h!]
\begin{center}
\subfloat[No b-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_et_10_shapes_postfit.pdf}}
\subfloat[B-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_et_13_shapes_postfit.pdf}}
\end{center}
\caption{High-\mT~control region in the (a) no b-tag and (b) b-tag categories of the \etau
channel. In the no b-tag category the \Wjets background, drawn together with the small
 di-boson plus single-top backgrounds as the `electroweak' background component, dominates. In the b-tag
category the \ttbar background is larger than the \Wjets background.}
\label{fig:bkgs_highmtctrl}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\subfloat[Pre-fit distribution]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/qcdosss_near_mt_1_prefit.png}}
\subfloat[Post-fit distribution]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/qcdosss_near_mt_1_postfit.png}}
\end{center}
\caption{The visible mass distribution of the di-$\tau$ pair in the \mutau channel for the sideband near the signal region, (a) before
the maximum likelihood fit to the QCD signal strenght and (b) after the fit. The resulting fitted signal strength 
is 1.180$\pm$0.044.}
\label{fig:mssm_qcdosss_mtnear}
\end{figure}

\begin{figure}[h!]
\begin{center}
\subfloat[Pre-fit distribution]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/qcdosss_far_mt_1_prefit.png}}
\subfloat[Post-fit distribution]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/qcdosss_far_mt_1_postfit.png}}
\end{center}
\caption{The visible mass distribution of the di-$\tau$ pair in the \mutau channel for the sideband further away from the signal region, (a) before
the maximum likelihood fit to the QCD signal strenght and (b) after the fit. The resulting fitted signal strength 
is 1.184$\pm$0.035.}
\label{fig:mssm_qcdosss_mtfar}
\end{figure}

>>>>

\begin{figure}[h!]
\begin{center}
\subfloat[Muon \pT]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/pt_1_inclusive_mt_2016.pdf}}
\subfloat[Electron $\eta$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/eta_1_inclusive_et_2016.pdf}}
\end{center}
\caption[The \pT~of the muon in the \mutau channel
and $\eta$ of the electron in the \etau channel, with the signal
overlaid.]{(a) \pT~of the muon in the \mutau channel and (b) $\eta$ of the electron in the \etau channel.
The gluon fusion (dashed blue line)
and b-associated (dashed purple line) signals are overlaid. The signals are normalised to 4000 times their
cross-section times branching ratio at \mA=1 TeV and \tanb=50 in the $m_{h}^{\text{mod+}}$ scenario.}
\label{fig:mt_muonpt}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\subfloat[$S/\sqrt{B}$]{\includegraphics[width=0.7\textwidth]{./MSSM/Figures/s_over_root_b_mt_m.png}}~\\
\subfloat[Size of error interval]{\includegraphics[width=0.7\textwidth]{./MSSM/Figures/mt_muons_iso_errint.png}}
\end{center}
\caption[The $S/\sqrt{B}$ for \Ztautau signal and
the size of the error interval on the best--fit value of a
maximum--likelihood fit to the \Ztautau signal strength, for various 
isolation selections.]{(a) The $S/\sqrt{B}$ for \Ztautau signal and (b) the size of the error interval on 
the best--fit value of a maximum--likelihood fit to the \Ztautau signal strength,
for various selections of the $\Delta\beta$--corrected
isolation variable with a cone size of $\Delta R = 0.4$ (solid circles), 
the $\Delta\beta$--corrected isolation variable with a cone size of $\Delta R = 0.3$ (open circles),
the $\Delta\beta$--corrected isolation variable including electrons and muons in the isolation
sum, for a cone size of $\Delta R =0.4$ (upward facing triangles) and $\Delta R =0.3$ (downward facing triangles) and
the tracker--based relative isolation (solid squares).}
\label{fig:mssm_selection_mt_muons}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\subfloat[$m_{\phi} = 160$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_160_range12.png}}
\subfloat[$m_{\phi} = 2.9$ TeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_2900_range12.png}}
%\subfloat[$m_{\phi} = 1600$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_1600_range12.pdf}}
%\subfloat[$m_{\phi} = 2900$ GeV]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/optimisation_ggh_mt_2900_range12.pdf}}
\end{center}
\caption[Pre--fit expected limit on $\sigma\times$BR for the gg$\phi$
production process with decay into $\Pgt\Pgt$ as a function of tau isolation 
working point and \mT~selection, for two mass points.]{Pre--fit expected limit on $\sigma\times$BR for the gg$\phi$ production process with decay into $\Pgt\Pgt$,
as a function of tau isolation working point (from very loose to very very tight) and
of \mT~selection from \mT$<20$ GeV to \mT$<40$ GeV, normalised to the best limit in the plane, indicated by the asterisk. This is shown
for (a) $m_{\phi}$ = 160 GeV and (b) $m_{\phi}$ = 2.9 TeV. The most optimal combination of \mT~selection and 
hadronic tau isolation working point varies, with looser selections preferred at higher mass.}
\label{fig:mssm_selection_mt_taumt}
\end{figure}
~
\begin{figure}[h!]
\begin{center}
\subfloat[gg$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_gradcuts_ggH_mt.pdf}}
\subfloat[bb$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_gradcuts_bbH_mt.pdf}}
\end{center}
\caption[Pre-fit expected limits on $\sigma \times$ BR for the gg$\phi$ and bb$\phi$
processes
in the
\mutau channel for an increasingly looser \mT~selection and tau isolation
working point.]{Pre-fit expected limits on $\sigma \times$ BR in the \mutau channel for (a) gg$\phi$ and
(b) bb$\phi$ production, for an increasingly looser \mT~selection and tau isolation working point, starting
at the tight working point and \mT$<30$ GeV in green, the medium working point and \mT$<40$ GeV in red,
the loose working point and \mT$<50$ GeV in blue and the very loose working point and \mT$<60$ GeV in black. Loosening
the tau isolation working point and \mT~selection gradually improves limits at higher mass, and
degrades them at low mass.}
\label{fig:mssm_gradcuts_mt}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\subfloat[gg$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_optimisation_mediummt40_vs_tightmt30pt20_mt_ggH_remake.pdf}}
\subfloat[bb$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_optimisation_mediummt40_vs_tightmt30pt20_mt_bbH_remake.pdf}}
\end{center}
\caption[Pre-fit expected limits on $\sigma\times$BR in the
\mutau channel for gg$\phi$ and bb$\phi$ prouduction, comparing
different hadronic tau \pT~cuts.]{Pre-fit expected limits on $\sigma\times$BR in the \mutau channel for (a) gg$\phi$ production and (b) bb$\phi$ production. The
limits when using the medium hadronic tau isolation working point and \mT$<40$ GeV selection using a minimum
hadronic tau \pT~selection of 20 GeV (red circles), 30 GeV (blue circles) and 40 GeV (black circles) are shown. The green
circles show the limits using tighter tau isolation working point and \mT~selection. The limits on
the gg$\phi$ production process improve at low masses when increasing the minimum hadronic tau \pT~selection,
the effect on the bb$\phi$ production process is less pronounced.}
\label{fig:mssm_tauptcut}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\subfloat[gg$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_gradcuts_ggH_et.pdf}}
\subfloat[bb$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_gradcuts_bbH_et.pdf}}
\end{center}
\caption[Pre-fit expected limits on $\sigma\times$ BR in the \etau
channel for gg$\phi$ and bb$\phi$ production for an increasingly
looser \mT~selection and tau isolation working point.]{Pre-fit expected limits on $\sigma \times$ BR in the \etau channel for (a) gg$\phi$ and
(b) bb$\phi$ production, for an increasingly looser \mT~selection and tau isolation working point, starting
at the tight working point and \mT$<40$ GeV in green, the medium working point and \mT$<50$ GeV in red,
the loose working point and \mT$<60$ GeV in blue and the very loose working point and \mT$<70$ GeV in black. Loosening
the tau isolation working point and \mT~selection gradually improves limits at higher mass, and
degrades them at low mass.}
\label{fig:mssm_gradcuts_et}
\end{figure}
\begin{figure}[h!]
\begin{center}
\subfloat[gg$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_optimisation_mediummt50_vs_tightmt40pt20_et_ggH_remake.pdf}}
\subfloat[bb$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_optimisation_mediummt50_vs_tightmt40pt20_et_bbH_remake.pdf}}
\end{center}
\caption[Pre-fit expected limits on $\sigma\times$BR in the \etau
channel for gg$\phi$ and bb$\phi$ production comparing different
hadronic tau isolation cuts.]{Pre-fit expected limits on $\sigma\times$BR in the \etau channel for (a) gg$\phi$ production and (b) bb$\phi$ production. The
limits using the medium hadronic tau isolation working point and \mT$<40$ GeV selection using a minimum
hadronic tau \pT~cut of 20 GeV (red circles), 30 GeV (blue circles) and 40 GeV (black circles) are shown. The green
circles show the limits using tighter tau isolation working point and \mT~selection. The limits on
the gg$\phi$ production process improve at low masses when increasing the hadronic tau \pT~cut,
the effect on the bb$\phi$ production process is less pronounced.}
\label{fig:mssm_tauptcut_et}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\subfloat[gg$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_thesis_ttopt_ggH.pdf}}
\subfloat[bb$\phi$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mssm_thesis_ttopt_bbH.pdf}}
\end{center}
\caption[Expected upper limits for the gg$\phi$ and bb$\phi$ process
in the \tautau channel, comparing different hadronic tau isolation working
points.]{Expected upper limits for (a) the gg$\phi$ process and (b) the bb$\phi$ process 
in the \tautau channel, using the 
medium (green), tight (red) and very tight working point of the tau isolation discriminator.
The pattern is roughly the same as in the \etau and \mutau channels, with looser selections preferred at high
mass.}
\label{fig:mssm_tauid_tt}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\subfloat[Reconstruction of $D_{\zeta}$]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/PZeta.pdf}}
\subfloat[$D_{\zeta}$ distribution in \emu channel]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/pzeta_inclusive_em_2016.pdf}}
\end{center}
\caption[Reconstruction of the $D_{\zeta}$ variable and the $D_{\zeta}$ distribution
in the \emu channel.]{(a) reconstruction of $D_{\zeta}$ \cite{cdf-dzeta} and (b) $D_{\zeta}$ distribution in the 
\emu channel\cite{CMS-PAS-HIG-16-037}.}
\label{fig:mssm_dzeta}
\end{figure}
~\clearpage
\subsection{Categorisation}
\label{sec:mssm_eventsel_categories}
As the analysis targets both the gluon fusion
and the b--associated production modes, 
the sensitivity to the signal can be increased by categorising
based on the number of b--tagged jets in the event.

\begin{figure}[h!]
\begin{center}
\subfloat[Number of jets]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/n_jets_inclusive_mt_2016_log.pdf}}
\subfloat[Number of b--tagged jets]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/n_bjets_inclusive_mt_2016_log.pdf}}
\end{center}
\caption[Number of jets and number of b-tagged jets in the \mutau channel, 
with the signal overlaid.]{(a) Number of jets and (b) number of b--tagged jets in the \mutau channel. The gluon fusion signal (dashed
blue line) and b--associated signal (dashed purple line) are overlaid on the expected background distribution. The signals
are normalised to 100 times their cross--section times branching ratio at \mA=1 TeV and \tanb=50 in the $m_{\text{h}}^{\text{mod+}}$
scenario. We can see how the signal--sensitive bins motivate the choice of categories.}
\label{fig:mssm_cats_mt}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\subfloat[QCD and signal in \tautau no b-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mttot_sigsep_tt_nobtag.pdf}}
\subfloat[\ttbar and signal in \emu b-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mttot_sigsep_em_btag.pdf}}
\end{center}
\caption[Total transverse mass distributions in the no b-tag category of the
\tautau channel for QCD and gluon fusion signal, and in the b-tag category
of the \emu channel, for \ttbar and b-associated signal.]{Total transverse mass distributions in (a) the no b-tag category of the \tautau
channel, for QCD and gluon fusion signal at 400 GeV and 1 and 2 TeV overlaid and (b) in the b-tag
category of the \emu channel, for \ttbar and b-associated signal at 400 GeV and 1 and 2 TeV. 
The total transverse mass variable separates the signal and these backgrounds well.}
\label{fig:mttot_sigseps}
\end{figure}

@@

\caption[\mTtot~distribution in the \ttbar
enriched control region, with and without applying top quark \pT~reweighting.]{\mTtot~distribution in the \ttbar enriched control region \MET>80 GeV and $D_{\zeta}<-20$ GeV in the \emu channel,

@@

\subsubsection*{Drell-Yan shape reweighting}
As the \ac{MC} samples used for the \Ztautau estimate
do not model the data well for events with high di-lepton
mass and high Z \pT, a reweighting is applied to correct for this.
These weights are derived in bins of $\PZ/\Pphotonx$ mass and \pT~
using \Zmm events in data, in such a way that they do not
change the overall Drell-Yan normalisation. The weights
are then applied to the \Ztautau and \Zellell background processes.
The mismodelling can be seen in figure \ref{fig:dyrwt}a, which
shows the observed data and expected background distribution of the \PZ \pT~in
\Zmm events. The overall effect of the reweighting, which is derived
based on the events shown in figure \ref{fig:dyrwt}a, on the \Ztautau background
shape in the no b-tag category of the \etau channel is shown in figure \ref{fig:dyrwt}b.
\begin{figure}[h!]
\begin{center}
\subfloat[\Zmm events]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/pt_tt_inclusive_zmm_2016_log_noweight.png}}
\subfloat[Effect of Drell-Yan shape reweighting on \Ztautau background]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/mttot_zttweight_et_nobtag.pdf}}
\end{center}
\caption[The mismodelling in the \PZ \pT~distribution as observed
in \Zmm events, and the impact of applying the Drell-Yan shape reweighting
on the total transverse mass distribution of the \Ztautau background in the no b-tag category of the \etau channel.]{(a) The mismodelling in the \PZ \pT~distribution as observed
in \Zmm events, used to derive the correction and (b) the impact of applying the Drell-Yan shape
reweighting on the total transverse
mass distribution of the \Ztautau background in the no b-tag category of the \etau channel.}
\label{fig:dyrwt}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\subfloat[\mutau no b-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/CMS-PAS-HIG-16-037_Figure-aux_001-a.pdf}}
\subfloat[\emu b-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/CMS-PAS-HIG-16-037_Figure-aux_003-b.pdf}}
\end{center}
\caption[The low \mTtot~region in the no b-tag category of the \mutau channel 
and in the b-tag category of the \emu channel.]{The low $m_{\text{T}}^{\text{tot}}$ region in (a) the 
no b-tag category of the \mutau channel and (b) the b-tag category of the \emu channel.
This low $m_{\text{T}}^{\text{tot}}$ region is where the backgrounds
are concentrated \cite{CMS-PAS-HIG-16-037-addit}.}
\label{fig:mssm_bkgs_overview}
\end{figure}

@@

The method described so far works well in the no b-tag categories, but in the b-tag category of both channels
the \ttbar background dominates. This is illustrated in figure \ref{fig:bkgs_highmtctrl}, where
the high-\mT~region in the no b-tag category (figure \ref{fig:bkgs_highmtctrl}a) is compared with the high-\mT~region in the 
b-tag category (figure \ref{fig:bkgs_highmtctrl}b) of the \etau channel. It is clear that the \ttbar 
background is much larger than the \Wjets background in the b-tag high-\mT~control region.
For this reason the estimate of the number
of \Wjets events in this category is made with a relaxed category selection where the b-tagging
requirement itself is removed, but the jet requirements still stand. Events with at least one 
jet with \pT$>20$ GeV and with $|\eta|<2.4$, but at most one jet with \pT$>30$ GeV and $|\eta|<4.7$, are therefore selected. The final \Wjets estimate in the b-tag category signal
region is determined by the estimate given by the number of \Wjets events
estimated in the 1-jet selection, multiplied by an extrapolation factor 
$\frac{N_{\text{W,MC}}^{\text{OS,low } m_{T},\text{b-tag category}}}{N_{\text{W,MC}}^{\text{OS, low }m_{\text{T}},\text{1-jet selection}}}$.
\begin{figure}[h!]
\begin{center}
\subfloat[No b-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_et_10_shapes_postfit.pdf}}
\subfloat[B-tag]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/htt_et_13_shapes_postfit.pdf}}
\end{center}
\caption[High-\mT~control region in the no b-tag and b-tag
categories of the \etau channel.]{High-\mT~control region in the (a) no b-tag and (b) b-tag categories of the \etau
channel. In the no b-tag category the \Wjets background, drawn together with the small
 di-boson plus single-top backgrounds as the `electroweak' background component, dominates. In the b-tag
category the \ttbar background is larger than the \Wjets background.}
\label{fig:bkgs_highmtctrl}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\subfloat[Pre-fit distribution]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/qcdosss_near_mt_1_prefit.png}}
\subfloat[Post-fit distribution]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/qcdosss_near_mt_1_postfit.png}}
\end{center}
\caption[The visible mass distribution of the di-$\tau$ pair
in the \mutau channel for the sideband near the signal region, before
and after the maximum likelihood fit to the QCD signal strength.]{The visible mass distribution of the di-$\tau$ pair in the \mutau channel for the sideband near the signal region, (a) before
the maximum likelihood fit to the QCD signal strenght and (b) after the fit. The resulting fitted signal strength 
is 1.180$\pm$0.044.}
\label{fig:mssm_qcdosss_mtnear}
\end{figure}

\begin{figure}[h!]
\begin{center}
\subfloat[Pre-fit distribution]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/qcdosss_far_mt_1_prefit.png}}
\subfloat[Post-fit distribution]{\includegraphics[width=0.5\textwidth]{./MSSM/Figures/qcdosss_far_mt_1_postfit.png}}
\end{center}
\caption[The visible mass distribution of the di-$\tau$ pair in the
\mutau channel for the sideband further away from the signal region,
before and after the maximum likelihood fit to the QCD signal strength.]{The visible mass distribution of the di-$\tau$ pair in the \mutau channel for the sideband further away from the signal region, (a) before
the maximum likelihood fit to the QCD signal strength and (b) after the fit. The resulting fitted signal strength 
is 1.184$\pm$0.035.}
\label{fig:mssm_qcdosss_mtfar}
\end{figure}
